
---
title: "Data Appendix"
author: "Your names here"
date: "Put the date here"
output: 
  html_document:
    code_folding: hide
    df_print: kable
---

#Due November 15 11:55pm on Moodle

note- do not change any part of the above after the `output` line! This time you can add to the R Markdown document you started with your project proposal to bring in the data, and to add a section for your data exploration. __Be sure  to have purpose, data, population, response variables, explanatory variables sections (which are from the initial proposal) reflect the comments that Miles made on your initial proposal.__


```{r message = FALSE, warning = FALSE}
# you may need to add more packages here
library(dplyr)
library(ggplot2)
library(readr)
```


# Data exploration

Once you have loaded in your data, You will create visualizations and summary statistics for each variable that you are interested in including in your project. __Do not do this for every variable in your data set__, just the variables you intend to use in your project.  

* Be sure to note missing values, unusual values, or other notable features of your data for each variable.  

* For each visualization or summary  statistic,  describe  in  words  what  the  visualization  or  summary  statistic tells us about that variable. For quantitative variables: are they skewed or symmetric? Are there outliers?

* Be sure you include data tables or a visualization showing the sample size for each level of your categorical variables (look back to the `group_by()` and `summarize()` examples in lab 5 & 6 and in the project tips file. 

* You will probably need to do some data wrangling at this phase of the project. Please see the project tips file on Moodle to help with assessing missing values, and some common data wranging tasks! 

* A tip: be sure to take a `glimpse()` of your data to check that the variables you **think** are quantitative are actually being treated as quantitative variables in R, and that you **think** are numeric are actually being treated as numeric in R.

```{r results = "hide"}
#glimpse()
```


```{r}
# put your data wrangling code here - be sure to make notes to yourself about what you are doing in each step!

```


## Variable 1: Name of variable is it response or explanatory, categorical or quantitative?

### summary statistics 


### data visualizations


***

## Variable 2: Name of variable is it response or explanatory, categorical or quantitative?

### summary statistics 

### data visualizations

***

##Repeat above for each variable you will actually analyze

__Only include the variables that you intend to use in your project__

