---
title: "Project Proposal"
author: " Madeleine Hickman, Christian Madrigal, Nukhbah Majid, Annabel Shein"
date: "11/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Data Appendix"
author: Madeleine Hickman, Christian Madrigal, Nukhbah Majid, Annabel Shein
date: November 18, 2019
output: 
  html_document:
    code_folding: hide
    df_print: kable
---

#Due November 15 11:55pm on Moodle

note- do not change any part of the above after the `output` line! This time you can add to the R Markdown document you started with your project proposal to bring in the data, and to add a section for your data exploration. __Be sure  to have purpose, data, population, response variables, explanatory variables sections (which are from the initial proposal) reflect the comments that Miles made on your initial proposal.__


```{r message = FALSE, warning = FALSE}
# you may need to add more packages here
library(dplyr)
library(ggplot2)
library(readr)
```

# Bechdel Test

**Group members:**   Madeleine Hickman, Christian Madrigal, Nukhbah Majid, Annabel Shein 

*** 

## Purpose 

The Bechdel test is a meausre of representation of women in fiction, and is used a lot for movies. A movie passes the Bechdel test if two women talk to each other about something other than a man, and sometimes the requirement that the women are named is added as well. We want to see trends in gender representaion in movies across genre and decade and seeing if there is a relationship in how well the movies do financially and if they pass the Bechdel test.

Some questions we have:
- Does the number of movies passing the Bechdel test change over time?
- Which genre of movie has the most movies that pass the Bechdel test?
- Does the gender of the director affect whether or not the movie passes the Bechdel test?
- Is there a relationship between the movie passing the Bechdel test and how much money the movie makes?

***

## The Data 

The data we plan to use is from the Fivethirtyeight library on R, the dataset is called Bechdel. This dataset has 1794 cases, which are movies form 1970 to 2013. We plan to exclude all  movies released prior to 1990 and use a random sample of 200 movies from this dataset. The Bechdel dataset is made up of movies that Fivethirtyeight analyzed, using data they collected form other sources. We are assuming that these movies were randomly drawn from all movies that were released from that time speriod for the sake of our project, but we know that this assumption probably won't stand.  


### Population  

The cases in our dataset are 200 movies, randomly sampled from our original dataset of movies released between 1990 and 2013. The population we are generalizing to is popular movies released between 1990 and 2013. We roughly estimate the population size to be 13,800 movies.



### Response Variables

Passing the Bechdel test (binary) (PASS/FAIL)
Domestic gross (USD, adjusted for inflation around dollar value in 2013)
International gross (USD, adjusted for inflation around dollar value in 2013)

What are the response variables? What are the units? Carefully define each variable and describe how each was measured. Estimate the range of possible values these variables may take on.  

> Note that you need to have at least 2 quantitative response variables

### Explanatory Variables
Passing the Bechdel test (binary) (PASS/FAIL)
Decade (ex: 90s, 2000s)
Director's gender (male/female)
Movie genre (Comedy, Action, Drama, Documentary, Other)
Budget (USD, adjusted for inflation around dollar value in 2013)

Describe the expanatory variables that you will use (i.e.  the columns of the data frame).  Carefully define each variable and describe how each was measured.  For categorical variables,  list  the  possible  categories;  for  quantitative  variables,  specify  the units of measurement.  

> Note on variables and cases: You need to have enough data to make meaningful inferences. There is no magic number of cases required for all projects. But aim for at least 100 cases and make sure there are at least 30 cases in each category of each of your categorical variables. Further, you will need to have at least 6 quantiative and 2 categorcal variables (If you only have quantitative variables, we can turn those into categorical, but remember that the reverse does not work)

