---
title: "Project Prototype"
author: "Nukhbah Majid"
date: "10/20/2019"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(dplyr)
library(tidyverse)
library(fivethirtyeight)
```

```{r}
bechdel <- bechdel
bechdel <- bechdel %>%
  filter(year >= 1990)
```

```{r}
set.seed(33)
sample1 <- sample_n(bechdel, 200)
```


```{r}
# Write the data to an excel file 
write_csv(sample1, 'bechdelSample.csv', col_names = TRUE)
```

```{r}
sample1 %>%
  summarise(mean = mean(domgross, na.rm = TRUE))
```

```{r}
try1 <- sample1 %>%
  group_by(year) %>%
  mutate(total = n()) %>%
  group_by(year, binary) %>%
  mutate(passNum = ifelse(binary == "PASS", n(), total-n() ) )
```

```{r}
ggplot(try1, aes(x= test))+
  geom_bar(fill = "skyblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
ggplot(try1, aes(x= binary))+
  geom_bar(fill = "lightpink")
```

The data visualizations above explore the `test` variable and the levels associated with the `test` categorical variable. The categories in the first graphic are explained below: 

* `ok` = passes test
* `dubious` = inconclusive result for reasons not explained by the dataset description. 
* `men` = women only talk about men
* `notalk` = women don't talk to each other
* `nowomen` = fewer than two women

The first graphic gives a rough idea that maybe more movies passed the bechdel test than the movies that failed the test. This misconception is cleared up by the second data graphic since the `binary` since it condenses the categories in `test` to either pass or fail labels for each of the movies. Hence, we see that more movies failed the bechdel test than pass it. 